\chapter{Appendix 1: God`s Morality Written into US Law}
\section{God`s Morality Written into US Law}

Although the United States is not a theocracy, the moral code of the Bible has been written into the laws of the land over time. The law is a tutor for morallity and the Bible is the ultimate source of morality.
Below are some examples of how the Bible has influenced US law.

\subsection{Murder and Theft}
Murder: "The unlawful killing of a human being by another with malice aforethought, either
express or implied."
\vspace{1\baselineskip}

\noindent Manslaughter: "The unlawful killing of another without malice, either express or implied; which may be either voluntarily, upon a sudden heat, or involuntarily, but in the commission of some unlawful act." \footnote{Black’s Law Dictionary. (1968). 4th ed. West Publishing Co.}

\vspace{2\baselineskip}


Unborn Victims Act of 1954


* Outlined further in chapter X. 



Though shalt not steal

\subsection{Perjury and False Witness}
Exodus 20:16



\subsection{Marriage and Family}

Add ref or docs to documents of founding charters etc 



\begin{scripture}[Isaiah 30:1-6]
    \vs{1}`Woe to the rebellious children,` declares the LORD, `Who execute a plan, but not Mine, And make an alliance, but not of My Spirit, In order to add sin to sin;
    \vs{2}Who proceed down to Egypt Without consulting Me, To take refuge in the safety of Pharaoh And to seek shelter in the shadow of Egypt!
    \vs{3}`Therefore the safety of Pharaoh will be your shame And the shelter in the shadow of Egypt, your humiliation.
    \vs{4}`For their princes are at Zoan And their ambassadors arrive at Hanes.
    \vs{5}`Everyone will be ashamed because of a people who cannot profit them, [Who are] not for help or profit, but for shame and also for reproach.`
    \vs{6}The oracle concerning the beasts of the Negev. Through a land of distress and anguish, From where [come] lioness and lion, viper and flying serpent, They carry their riches on the backs of young donkeys And their treasures on camels` humps, To a people who cannot profit [them];
\end{scripture}
