\chapter{Origin of Life}

\marginnote{\textbf{Q1:} In the following passage was the baby (John the Babptist) concious of 
his sorroundings?}

\begin{scripture}[Luke 1:41-44]
    \ch{1}When Elizabeth heard Mary's greeting, the baby leaped in her womb; and Elizabeth was filled with the Holy Spirit.    \begin{poetry}
        \vs{42}And she cried out with a loud voice and said, 'Blessed [are] you among women, and blessed [is] the fruit of your womb!
        \vs{43}And how has it [happened] to me, that the mother of my Lord would come to me?
        \vs{44}For behold, when the sound of your greeting reached my ears, the baby leaped in my womb for joy.    \end{poetry}
\end{scripture}

\marginnote{\textbf{Q2:} In light of \textbf{2 Timothy 3:16} (see introduction) what might be God's purpose in recording this moment into the Gospel of Luke?}


\vspace{6\baselineskip}



\begin{scripture}[Psalm 139:13-16]
    \marginnote{\textbf{Q3:} Who controls has ultimate control over a woman's body?}

    \ch{139}For You formed my inward parts; You wove me in my mother's womb.  
        \vs{14}I will give thanks to You, for I am fearfully and wonderfully made; Wonderful are Your works, And my soul knows it very well.
        \vs{15}My frame was not hidden from You, When I was made in secret, [And] skillfully wrought in the depths of the earth;
        \vs{16}Your eyes have seen my unformed substance; And in Your book were all written The days that were ordained [for me], When as yet there was not one of them.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[Genesis 29:31]
    \vs{31}Now the LORD saw that Leah was unloved, and He opened her womb, but Rachel was barren.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[Genesis 30:22]
    \vs{22}Then God remebered Rachel, and God gave heed to her and opened her womb.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[1 Samuel 1:5-6]
    \vs{5}but to Hannah he would give a double portion, for he loved Hannah, but the LORD had closed her womb.
    \vs{6}Her rival, however, would provoke her bitterly to irritate her, because the LORD had closed her womb.
\end{scripture}

\vspace{2\baselineskip}

