\chapter{Faithfullness}

Is believing enough? Is believing in Pro-Life principles sufficient to be faithful to God?

\begin{scripture}[Micah 6:8]
    \vs{8}He has told you, O man, what is good; And what does the LORD require of you But to do justice, to love kindness, And to walk humbly with your God?
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[Proverbs 31:8-9]
    \vs{8}Open your mouth for the mute, For the rights of all the unfortunate.
    \vs{9}Open your mouth, judge righteously, And defend the rights of the afflicted and needy.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[1 Samuel 15:22]
    \vs{22}Samuel said, 'Has the LORD as much delight in burnt offerings and sacrifices As in obeying the voice of the LORD? Behold, to obey is better than sacrifice, [And] to heed than the fat of rams.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[Deuteronomy 10:12-13]
    \vs{12}'Now, Israel, what does the LORD your God require from you, but to fear the LORD your God, to walk in all His ways and love Him, and to serve the LORD your God with all your heart and with all your soul,
    \vs{13}[and] to keep the LORD'S commandments and His statutes which I am commanding you today for your good?
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[Proverbs 14:23]
    \vs{23}In all labor there is profit, But mere talk [leads] only to poverty.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[1 John 3:18]
    \vs{18}Little children, let us not love with word or with tongue, but in deed and truth.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[Ephesians 5:11]
    \vs{11}Do not participate in the unfruitful deeds of darkness, but instead even expose them;
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[James 1:22-25]
    \vs{22}But prove yourselves doers of the word, and not merely hearers who delude themselves.
    \vs{23}For if anyone is a hearer of the word and not a doer, he is like a man who looks at his natural face in a mirror;
    \vs{24}for [once] he has looked at himself and gone away, he has immediately forgotten what kind of person he was.
    \vs{25}But one who looks intently at the perfect law, the [law] of liberty, and abides by it, not having become a forgetful hearer but an effectual doer, this man will be blessed in what he does.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[1 Peter 3:14-17]
    \vs{14}But even if you should suffer for the sake of righteousness, you are blessed. AND DO NOT FEAR THEIR INTIMIDATION, AND DO NOT BE TROUBLED,
    \vs{15}but sanctify Christ as Lord in your hearts, always [being] ready to make a defense to everyone who asks you to give an account for the hope that is in you, yet with gentleness and reverence;
    \vs{16}and keep a good conscience so that in the thing in which you are slandered, those who revile your good behavior in Christ will be put to shame.
    \vs{17}For it is better, if God should will it so, that you suffer for doing what is right rather than for doing what is wrong.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[Matthew 5:10-12]
    \vs{10}'Blessed are those who have been persecuted for the sake of righteousness, for theirs is the kingdom of heaven.
    \vs{11}'Blessed are you when [people] insult you and persecute you, and falsely say all kinds of evil against you because of Me.
    \vs{12}'Rejoice and be glad, for your reward in heaven is great; for in the same way they persecuted the prophets who were before you.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[1 Peter 4:12-16]
    \vs{12}Beloved, do not be surprised at the fiery ordeal among you, which comes upon you for your testing, as though some strange thing were happening to you;
    \vs{13}but to the degree that you share the sufferings of Christ, keep on rejoicing, so that also at the revelation of His glory you may rejoice with exultation.
    \vs{14}If you are reviled for the name of Christ, you are blessed, because the Spirit of glory and of God rests on you.
    \vs{15}Make sure that none of you suffers as a murderer, or thief, or evildoer, or a troublesome meddler;
    \vs{16}but if [anyone suffers] as a Christian, he is not to be ashamed, but is to glorify God in this name.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[John 16:33]
    \vs{33}'These things I have spoken to you, so that in Me you may have peace. In the world you have tribulation, but take courage; I have overcome the world.'
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[John 17:14-16]
    \vs{14}'I have given them Your word; and the world has hated them, because they are not of the world, even as I am not of the world.
    \vs{15}'I do not ask You to take them out of the world, but to keep them from the evil [one].
    \vs{16}'They are not of the world, even as I am not of the world.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[Matthew 10:34-36]
    \vs{34}'Do not think that I came to bring peace on the earth; I did not come to bring peace, but a sword.
    \vs{35}'For I came to SET A MAN AGAINST HIS FATHER, AND A DAUGHTER AGAINST HER MOTHER, AND A DAUGHTER-IN-LAW AGAINST HER MOTHER-IN-LAW;
    \vs{36}and A MAN'S ENEMIES WILL BE THE MEMBERS OF HIS HOUSEHOLD.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[Romans 12:18]
    \vs{18}If possible, so far as it depends on you, be at peace with all men.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[Matthew 5:9]
    \vs{9}'Blessed are the peacemakers, for they shall be called sons of God.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[James 3:17-18]
    \vs{17}But the wisdom from above is first pure, then peaceable, gentle, reasonable, full of mercy and good fruits, unwavering, without hypocrisy.
    \vs{18}And the seed whose fruit is righteousness is sown in peace by those who make peace.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[1 Corinthians 1:18]
    \vs{18}For the word of the cross is foolishness to those who are perishing, but to us who are being saved it is the power of God.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[Galatians 1:10]
    \vs{10}For am I now seeking the favor of men, or of God? Or am I striving to please men? If I were still trying to please men, I would not be a bond-servant of Christ.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[John 15:18-20]
    \vs{18}'If the world hates you, you know that it has hated Me before [it hated] you.
    \vs{19}'If you were of the world, the world would love its own; but because you are not of the world, but I chose you out of the world, because of this the world hates you.
    \vs{20}'Remember the word that I said to you, 'A slave is not greater than his master.' If they persecuted Me, they will also persecute you; if they kept My word, they will keep yours also.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[Ephesians 5:11]
    \vs{11}Do not participate in the unfruitful deeds of darkness, but instead even expose them;
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[Leviticus 19:15]
    \vs{15}'You shall do no injustice in judgment; you shall not be partial to the poor nor defer to the great, but you are to judge your neighbor fairly.
\end{scripture}
