\chapter{Imposed Morality}

\begin{fullwidth}
Some people say that America is not a christian nation, therefore we should not impose "our" morals on society. Abortion has been 
tagged a political issue and as such, we are told we should keep it out of the pulpit. Often pastors are scared to speak God`s truth on the subjects that have been marked as political for fear of losing half their congregation. 
Do we as believers in America have more alegiance to God or to the construct of `seperation of church and state`? Is it even possible for a 
righteous believer to seperate their faith from their politics? Let`s see what God`s word says about believers living in a nation that appears to be drifting further and further from God`s will.
\end{fullwidth}


\section{God`s People Looking at Foreign Nations}
"America isn`t Israel, we can`t expect it to follow God`s moral code."  This is a sentiment often expressed by people more concerened with the seperation of church and state than they are God`s will for the nations.
God can and will hold nations accountable for their actions even if they are not specifically run by His "chosen" people. 

\begin{scripture}[Deuteronomy 23:3]
    \vs{3}\marginnote{\question{CHEKC VERSION}}
    No Ammonite or Moabite shall enter the assembly of the LORD; none of their descendants, even to the tenth generation, shall ever enter the assembly of the LORD,
\end{scripture}

\begin{scripture}[Amos 1:13-15]
    \vs{13}Thus says the LORD, `For three transgressions of the sons of Ammon and for four I will not revoke its [punishment], Because they ripped open the pregnant women of Gilead In order to enlarge their borders.
    \vs{14}`So I will kindle a fire on the wall of Rabbah And it will consume her citadels Amid war cries on the day of battle, And a storm on the day of tempest.
    \vs{15}`Their king will go into exile, He and his princes together,` says the LORD. 
    \marginnote{\question{Was God watching the actions of the Ammonites?  What did he promise to do to them?}}
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[Psalm 96:5]
    \vs{5} \marginnote{\question{Why would God care what people who don`t claim to represent him do with their lives?}}
    For all the gods of the peoples are idols, But the LORD made the heavens.
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[Leviticus 18:24-30]
    \vs{24}    \marginnote{\question{What abominations was God speaking about?}}

    `Do not defile yourselves by any of these things; for by all these the nations which I am casting out before you have become defiled.
    \vs{25}`For the land has become defiled, therefore I have brought its punishment upon it, so the land has spewed out its inhabitants.
    \vs{26}`But as for you, you are to keep My statutes and My judgments and shall not do any of these abominations, [neither] the native, nor the alien who sojourns among you
    \vs{27}(for the men of the land who have been before you have done all these abominations, and the land has become defiled);
    \vs{28}so that the land will not spew you out, should you defile it, as it has spewed out the nation which has been before you.
    \marginnote{\question{Is it possible that our land has been defiled due to the abominations we have accepted as normal? If so, what might that mean for those who live in America?}}

    \vs{29}`For whoever does any of these abominations, those persons who do [so] shall be cut off from among their people.
    \vs{30}`Thus you are to keep My charge, that you do not practice any of the abominable customs which have been practiced before you, so as not to defile yourselves with them; I am the LORD your God.``
\end{scripture}

\vspace{4\baselineskip}

\marginnote{\question{God tells the Israelites to keep His commandments and to avoid falling into the sins of those who don`t know God. Can you think of any reason why this sentiment would not apply to modern followers of Christ?}}



\section{God`s People Living in a Foreign Land}

\begin{scripture}[Philippians 2:14-16]
    \vs{14}\marginnote{\question{A common definition of above reproach is to conduct yourself in such a way that no one can accuse you of wrong doing or immorality.
     Are you able to be above reproach if people don`t know what you believe?}}
    Do all things without grumbling or disputing;
    \vs{15}so that you will prove yourselves to be blameless and innocent, children of God above reproach in the midst of a crooked and perverse generation, among whom you appear as lights in the world,
    \vs{16}holding fast the word of life, so that in the day of Christ I will have reason to glory because I did not run in vain nor toil in vain.
\end{scripture}

\marginnote{\question{What would some characteristics of a crooked and perverse generation be? Are we living in one?}}
\vspace{2\baselineskip}

\begin{scripture}[Matthew 5:13-16]
    \vs{13}\marginnote{\question{What would the life of a person who`s salt is tasteless look like?}}
    `You are the salt of the earth; but if the salt has become tasteless, how can it be made salty [again]? It is no longer good for anything, except to be thrown out and trampled under foot by men.
    \vs{14}`You are the light of the world. A city set on a hill cannot be hidden;
    \vs{15}nor does [anyone] light a lamp and put it under a basket, but on the lampstand, and it gives light to all who are in the house.
    \vs{16}`Let your light shine before men in such a way that they may see your good works, and glorify your Father who is in heaven.
    \marginnote{\question{Many people believe that simply existing as a Christian is enough to be a light in the world. What does this passage say about that?}}
\end{scripture}

    \begin{scripture}[Ephesians 5:8-11]
        \vs{8}for you were once darkness, but now you are light in the Lord; walk as children of light
        \vs{9}(for the fruit of the light consists in all goodness, righteousness, and truth),
        \vs{10}as you try to learn what is pleasing to the Lord.
        \vs{11}Do not participate in the useless deeds of darkness, but instead even expose them;
        \vs{12}for it is disgraceful even to speak of the things which are done by them in secret.
        \vs{13}But all things become visible when they are exposed by the light, for everything that becomes visible is light.
    \end{scripture}

\vspace{2\baselineskip}

\marginnote{\question{One of the purposes of light is to expose darkness. Do people know you as someone hwo speaks against the evil in the world?}}

\vspace{2\baselineskip}

\marginnote{\question{Does God expect us to live differently than the world? Do you need to start living differently? If so what do you need to start doing? Be specific.}}


\section{God`s People Affected by Foreign Influence}

\begin{scripture}[Isaiah 2:6-8]
    \vs{6}For You have abandoned Your people, \marginnote{\question{What does it look like when God`s people act in disobedience?}}
    the house of Jacob, Because they are filled [with influences] from the east, And [they are] soothsayers like the Philistines, And they strike [bargains] with the children of foreigners.
    \vs{7}Their land has also been filled with silver and gold And there is no end to their treasures; Their land has also been filled with horses And there is no end to their chariots.
    \vs{8}Their land has also been filled with idols; They worship the work of their hands, That which their fingers have made.
    \marginnote{\question{From the beginning of history, God`s people were charged with the governance of their nation in accordance to God`s character and values. In a 
    similar vein sp?? 9 out of the original thirteen American colonies had law which required that those who held governmental positions had to be of Christian faith. 
    Do you think Isaiah 2:6-8 tells the story of what has happened in America in the last 400 years? If so, what does faithfulness look like in our modern context?}}
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[Romans 12:2]
    \vs{2} \marginnote{\question{In what you conformed to the world? Or have you been transformed by the renewal of your mind?}}
    And do not be conformed to this world, but be transformed by the renewing of your mind, so that you may prove what the will of God is, that which is good and acceptable and perfect.
\end{scripture}

\vspace{4\baselineskip}
\marginnote{\question{Society has tells us that abortion is healthcare and tan abortion ought to be a woman`s right. How have you been influenced by these lies?}}


\begin{scripture}[1 John 2:15-17]
    \vs{15}Do not love the world nor the things in the world. If anyone loves the world, the love of the Father is not in him.
    \vs{16}For all that is in the world, the lust of the flesh and the lust of the eyes and the boastful pride of life, is not from the Father, but is from the world.
    \vs{17}The world is passing away, and [also] its lusts; but the one who does the will of God lives forever.\marginnote{\question{Are you doing the will of God? How do you know?}}
\end{scripture}

\vspace{2\baselineskip}

\begin{scripture}[1 Peter 2:9-12]
    \vs{9}But you are A CHOSEN RACE, \marginnote{\question{As people who have received tremendous mercy, what are we to do according to this passage?}}
     A royal PRIESTHOOD, A HOLY NATION, A PEOPLE FOR [God`s] OWN POSSESSION, so that you may proclaim the excellencies of Him who has called you out of darkness into His marvelous light;
    \vs{10}for you once were NOT A PEOPLE, but now you are THE PEOPLE OF GOD; you had NOT RECEIVED MERCY, but now you have RECEIVED MERCY.
    \vs{11}Beloved, I urge you as aliens and strangers to abstain from fleshly lusts which wage war against the soul.
    \vs{12}Keep your behavior excellent among the Gentiles, so that in the thing in which they slander you as evildoers, they may because of your good deeds, as they observe [them], glorify God in the day of visitation.
\end{scripture}
\marginnote{\question{Followers of Christ are called a CHOSEN RACE... set apart for God`s possession. Does this change the way you think about the family of God?
How does this passage change the way you think about your role in society?}}

\vspace{2\baselineskip}
