\chapter{Who is my neighbor?}

God's greatest commandments are to love Him and to love our neighbors as ourselves. But who is our neighbor? The Bible gives us a clear answer to this question.


\begin{scripture}[Leviticus 19:18]
    \vs{18}'You shall not take vengeance, nor bear any grudge against the sons of your people, but you shall love your neighbor as yourself; I am the LORD.
\end{scripture}

\begin{scripture}[Matthew 22:37-40]
    \vs{37}And He said to him, ''YOU SHALL LOVE THE LORD YOUR GOD WITH ALL YOUR HEART, AND WITH ALL YOUR SOUL, AND WITH ALL YOUR MIND.'
    \vs{38}'This is the great and foremost commandment.
    \vs{39}'The second is like it, 'YOU SHALL LOVE YOUR NEIGHBOR AS YOURSELF.'
    \vs{40}'On these two commandments depend the whole Law and the Prophets.'
\end{scripture}

\begin{scripture}[Luke 10:29-37]
    \vs{29}But wishing to justify himself, he said to Jesus, 'And who is my neighbor?'
    \vs{30}Jesus replied and said, 'A man was going down from Jerusalem to Jericho, and fell among robbers, and they stripped him and beat him, and went away leaving him half dead.
    \vs{31}'And by chance a priest was going down on that road, and when he saw him, he passed by on the other side.
    \vs{32}'Likewise a Levite also, when he came to the place and saw him, passed by on the other side.
    \vs{33}'But a Samaritan, who was on a journey, came upon him; and when he saw him, he felt compassion,
    \vs{34}and came to him and bandaged up his wounds, pouring oil and wine on [them]; and he put him on his own beast, and brought him to an inn and took care of him.
    \vs{35}'On the next day he took out two denarii and gave them to the innkeeper and said, 'Take care of him; and whatever more you spend, when I return I will repay you.'
    \vs{36}'Which of these three do you think proved to be a neighbor to the man who fell into the robbers' [hands]?'
    \vs{37}And he said, 'The one who showed mercy toward him.' Then Jesus said to him, 'Go and do the same.'
\end{scripture}

\begin{scripture}[James 2:8-9]
    \vs{8}If, however, you are fulfilling the royal law according to the Scripture, 'YOU SHALL LOVE YOUR NEIGHBOR AS YOURSELF,' you are doing well.
    \vs{9}But if you show partiality, you are committing sin [and] are convicted by the law as transgressors.
\end{scripture}

\begin{scripture}[Galatians 3:28]
    \vs{28}There is neither Jew nor Greek, there is neither slave nor free man, there is neither male nor female; for you are all one in Christ Jesus.
\end{scripture}

\begin{scripture}[Galatians 5:14]
    \vs{14}For the whole Law is fulfilled in one word, in the [statement], 'YOU SHALL LOVE YOUR NEIGHBOR AS YOURSELF.'
\end{scripture}

\begin{scripture}[Romans 13:8-10]
    \vs{8}Owe nothing to anyone except to love one another; for he who loves his neighbor has fulfilled [the] law.
    \vs{9}For this, 'YOU SHALL NOT COMMIT ADULTERY, YOU SHALL NOT MURDER, YOU SHALL NOT STEAL, YOU SHALL NOT COVET,' and if there is any other commandment, it is summed up in this saying, 'YOU SHALL LOVE YOUR NEIGHBOR AS YOURSELF.'
    \vs{10}Love does no wrong to a neighbor; therefore love is the fulfillment of [the] law.
\end{scripture}

\begin{scripture}[Matthew 5:43-44]
    \vs{43}'You have heard that it was said, 'YOU SHALL LOVE YOUR NEIGHBOR and hate your enemy.'
    \vs{44}'But I say to you, love your enemies and pray for those who persecute you,
\end{scripture}
