\begin{scripture}[Genesis 1:18-28]
    \vs{18}and to govern the day and the night, and to separate the light from the darkness; and God saw that it was good.
    \vs{19}There was evening and there was morning, a fourth day.
    \vs{20}Then God said, 'Let the waters teem with swarms of living creatures, and let birds fly above the earth in the open expanse of the heavens.'
    \vs{21}God created the great sea monsters and every living creature that moves, with which the waters swarmed after their kind, and every winged bird after its kind; and God saw that it was good.
    \vs{22}God blessed them, saying, 'Be fruitful and multiply, and fill the waters in the seas, and let birds multiply on the earth.'
    \vs{23}There was evening and there was morning, a fifth day.
    \vs{24}Then God said, 'Let the earth bring forth living creatures after their kind: cattle and creeping things and beasts of the earth after their kind'; and it was so.
    \vs{25}God made the beasts of the earth after their kind, and the cattle after their kind, and everything that creeps on the ground after its kind; and God saw that it was good.
    \vs{26}Then God said, 'Let Us make man in Our image, according to Our likeness; and let them rule over the fish of the sea and over the birds of the sky and over the cattle and over all the earth, and over every creeping thing that creeps on the earth.'
    \vs{27}God created man in His own image, in the image of God He created him; male and female He created them.
    \vs{28}God blessed them; and God said to them, 'Be fruitful and multiply, and fill the earth, and subdue it; and rule over the fish of the sea and over the birds of the sky and over every living thing that moves on the earth.'
\end{scripture}

\begin{scripture}[Ecclesiastes 3:11]
    \vs{11}He has made everything appropriate in its time. He has also set eternity in their heart, yet so that man will not find out the work which God has done from the beginning even to the end.
\end{scripture}

\begin{scripture}[John 3:16]
    \vs{16}'For God so loved the world, that He gave His only begotten Son, that whoever believes in Him shall not perish, but have eternal life.
\end{scripture}

\begin{scripture}[Romans 6:23]
    \vs{23}For the wages of sin is death, but the free gift of God is eternal life in Christ Jesus our Lord.
\end{scripture}

\begin{scripture}[Matthew 25:46]
    \vs{46}'These will go away into eternal punishment, but the righteous into eternal life.'
\end{scripture}

\begin{scripture}[2 Corinthians 5:10]
    \vs{10}For we must all appear before the judgment seat of Christ, so that each one may be recompensed for his deeds in the body, according to what he has done, whether good or bad.
\end{scripture}

\begin{scripture}[Daniel 12:2]
    \vs{2}'Many of those who sleep in the dust of the ground will awake, these to everlasting life, but the others to disgrace [and] everlasting contempt.
\end{scripture}

\begin{scripture}[Revelation 22:5]
    \vs{5}And there will no longer be [any] night; and they will not have need of the light of a lamp nor the light of the sun, because the Lord God will illumine them; and they will reign forever and ever.
\end{scripture}

\begin{scripture}[Leviticus 24:17-22]
    \vs{17}'If a man takes the life of any human being, he shall surely be put to death.
    \vs{18}'The one who takes the life of an animal shall make it good, life for life.
    \vs{19}'If a man injures his neighbor, just as he has done, so it shall be done to him:
    \vs{20}fracture for fracture, eye for eye, tooth for tooth; just as he has injured a man, so it shall be inflicted on him.
    \vs{21}'Thus the one who kills an animal shall make it good, but the one who kills a man shall be put to death.
    \vs{22}'There shall be one standard for you; it shall be for the stranger as well as the native, for I am the LORD your God.''
\end{scripture}

\begin{scripture}[Ephesians 2:10]
    \vs{10}For we are His workmanship, created in Christ Jesus for good works, which God prepared beforehand so that we would walk in them.
\end{scripture}

\begin{scripture}[Leviticus 19:15]
    \vs{15}'You shall do no injustice in judgment; you shall not be partial to the poor nor defer to the great, but you are to judge your neighbor fairly.
\end{scripture}

\begin{scripture}[Galatians 3:25-30]
    \vs{25}But now that faith has come, we are no longer under a tutor.
    \vs{26}For you are all sons of God through faith in Christ Jesus.
    \vs{27}For all of you who were baptized into Christ have clothed yourselves with Christ.
    \vs{28}There is neither Jew nor Greek, there is neither slave nor free man, there is neither male nor female; for you are all one in Christ Jesus.
    \vs{29}And if you belong to Christ, then you are Abraham's descendants, heirs according to promise.
\end{scripture}

\begin{scripture}[Exodus 23:2-9]
    \vs{2}'You shall not follow the masses in doing evil, nor shall you testify in a dispute so as to turn aside after a multitude in order to pervert [justice];
    \vs{3}nor shall you be partial to a poor man in his dispute.
    \vs{4}'If you meet your enemy's ox or his donkey wandering away, you shall surely return it to him.
    \vs{5}'If you see the donkey of one who hates you lying [helpless] under its load, you shall refrain from leaving it to him, you shall surely release [it] with him.
    \vs{6}'You shall not pervert the justice [due] to your needy [brother] in his dispute.
    \vs{7}'Keep far from a false charge, and do not kill the innocent or the righteous, for I will not acquit the guilty.
    \vs{8}'You shall not take a bribe, for a bribe blinds the clear-sighted and subverts the cause of the just.
    \vs{9}'You shall not oppress a stranger, since you yourselves know the feelings of a stranger, for you [also] were strangers in the land of Egypt.
\end{scripture}

\begin{scripture}[Proverbs 31:8-9]
    \vs{8}Open your mouth for the mute, For the rights of all the unfortunate.
    \vs{9}Open your mouth, judge righteously, And defend the rights of the afflicted and needy.
\end{scripture}

\begin{scripture}[Leviticus 19:15]
    \vs{15}'You shall do no injustice in judgment; you shall not be partial to the poor nor defer to the great, but you are to judge your neighbor fairly.
\end{scripture}

\begin{scripture}[Luke 4:18]
    \vs{18}'THE SPIRIT OF THE LORD IS UPON ME, BECAUSE HE ANOINTED ME TO PREACH THE GOSPEL TO THE POOR. HE HAS SENT ME TO PROCLAIM RELEASE TO THE CAPTIVES, AND RECOVERY OF SIGHT TO THE BLIND, TO SET FREE THOSE WHO ARE OPPRESSED,
\end{scripture}

\begin{scripture}[Luke 9:49-50]
    \vs{49}John answered and said, 'Master, we saw someone casting out demons in Your name; and we tried to prevent him because he does not follow along with us.'
    \vs{50}But Jesus said to him, 'Do not hinder [him]; for he who is not against you is for you.'
\end{scripture}

\begin{scripture}[Luke 10:38-39]
    \vs{38}Now as they were traveling along, He entered a village; and a woman named Martha welcomed Him into her home.
    \vs{39}She had a sister called Mary, who was seated at the Lord's feet, listening to His word.
\end{scripture}

\begin{scripture}[Luke 1:41-44]
    \vs{41}When Elizabeth heard Mary's greeting, the baby leaped in her womb; and Elizabeth was filled with the Holy Spirit.
    \vs{42}And she cried out with a loud voice and said, 'Blessed [are] you among women, and blessed [is] the fruit of your womb!
    \vs{43}'And how has it [happened] to me, that the mother of my Lord would come to me?
    \vs{44}'For behold, when the sound of your greeting reached my ears, the baby leaped in my womb for joy.
\end{scripture}

\begin{scripture}[Psalm 139:13-16]
    \vs{13}For You formed my inward parts; You wove me in my mother's womb.
    \vs{14}I will give thanks to You, for I am fearfully and wonderfully made; Wonderful are Your works, And my soul knows it very well.
    \vs{15}My frame was not hidden from You, When I was made in secret, [And] skillfully wrought in the depths of the earth;
    \vs{16}Your eyes have seen my unformed substance; And in Your book were all written The days that were ordained [for me], When as yet there was not one of them.
\end{scripture}

\begin{scripture}[Genesis 29:31]
    \vs{31}Now the LORD saw that Leah was unloved, and He opened her womb, but Rachel was barren.
\end{scripture}

\begin{scripture}[Genesis 30:22]
    \vs{22}Then God remembered Rachel, and God gave heed to her and opened her womb.
\end{scripture}

\begin{scripture}[1 Samuel 1:5-6]
    \vs{5}but to Hannah he would give a double portion, for he loved Hannah, but the LORD had closed her womb.
    \vs{6}Her rival, however, would provoke her bitterly to irritate her, because the LORD had closed her womb.
\end{scripture}

\begin{scripture}[Isaiah 49:1]
    \vs{1}Listen to Me, O islands, And pay attention, you peoples from afar. The LORD called Me from the womb; From the body of My mother He named Me.
\end{scripture}

\begin{scripture}[Jeremiah 1:5]
    \vs{5}'Before I formed you in the womb I knew you, And before you were born I consecrated you; I have appointed you a prophet to the nations.'
\end{scripture}

\begin{scripture}[Genesis 25:22-23]
    \vs{22}But the children struggled together within her; and she said, 'If it is so, why then am I [this way]?' So she went to inquire of the LORD.
    \vs{23}The LORD said to her, 'Two nations are in your womb; And two peoples will be separated from your body; And one people shall be stronger than the other; And the older shall serve the younger.'
\end{scripture}

\begin{scripture}[Galatians 1:15]
    \vs{15}But when God, who had set me apart [even] from my mother's womb and called me through His grace, was pleased
\end{scripture}

\begin{scripture}[Exodus 21:22-25]
    \vs{22}'If men struggle with each other and strike a woman with child so that she gives birth prematurely, yet there is no injury, he shall surely be fined as the woman's husband may demand of him, and he shall pay as the judges [decide].
    \vs{23}'But if there is [any further] injury, then you shall appoint [as a penalty] life for life,
    \vs{24}eye for eye, tooth for tooth, hand for hand, foot for foot,
    \vs{25}burn for burn, wound for wound, bruise for bruise.
\end{scripture}

\begin{scripture}[Luke 1:20-25]
    \vs{20}'And behold, you shall be silent and unable to speak until the day when these things take place, because you did not believe my words, which will be fulfilled in their proper time.'
    \vs{21}The people were waiting for Zacharias, and were wondering at his delay in the temple.
    \vs{22}But when he came out, he was unable to speak to them; and they realized that he had seen a vision in the temple; and he kept making signs to them, and remained mute.
    \vs{23}When the days of his priestly service were ended, he went back home.
    \vs{24}After these days Elizabeth his wife became pregnant, and she kept herself in seclusion for five months, saying,
    \vs{25}'This is the way the Lord has dealt with me in the days when He looked [with favor] upon [me], to take away my disgrace among men.'
\end{scripture}

\begin{scripture}[1 Samuel 1:27]
    \vs{27}'For this boy I prayed, and the LORD has given me my petition which I asked of Him.
\end{scripture}

\begin{scripture}[Job 3:1-9]
    \vs{1}Afterward Job opened his mouth and cursed the day of his [birth].
    \vs{2}And Job said,
    \vs{3}'Let the day perish on which I was to be born, And the night [which] said, 'A boy is conceived.'
    \vs{4}'May that day be darkness; Let not God above care for it, Nor light shine on it.
    \vs{5}'Let darkness and black gloom claim it; Let a cloud settle on it; Let the blackness of the day terrify it.
    \vs{6}'[As for] that night, let darkness seize it; Let it not rejoice among the days of the year; Let it not come into the number of the months.
    \vs{7}'Behold, let that night be barren; Let no joyful shout enter it.
    \vs{8}'Let those curse it who curse the day, Who are prepared to rouse Leviathan.
    \vs{9}'Let the stars of its twilight be darkened; Let it wait for light but have none, And let it not see the breaking dawn;
\end{scripture}

\begin{scripture}[Job 3:10-16]
    \vs{10}Because it did not shut the opening of my [mother's] womb, Or hide trouble from my eyes.
    \vs{11}'Why did I not die at birth, Come forth from the womb and expire?
    \vs{12}'Why did the knees receive me, And why the breasts, that I should suck?
    \vs{13}'For now I would have lain down and been quiet; I would have slept then, I would have been at rest,
    \vs{14}With kings and [with] counselors of the earth, Who rebuilt ruins for themselves;
    \vs{15}Or with princes who had gold, Who were filling their houses [with] silver.
    \vs{16}'Or like a miscarriage which is discarded, I would not be, As infants that never saw light.
\end{scripture}

\begin{scripture}[Exodus 20:13]
    \vs{13}'You shall not murder.
\end{scripture}

\begin{scripture}[Genesis 9:6]
    \vs{6}'Whoever sheds man's blood, By man his blood shall be shed, For in the image of God He made man.
\end{scripture}

\begin{scripture}[Numbers 35:22-25]
    \vs{22}'But if he pushed him suddenly without enmity, or threw something at him without lying in wait,
    \vs{23}or with any deadly object of stone, and without seeing it dropped on him so that he died, while he was not his enemy nor seeking his injury,
    \vs{24}then the congregation shall judge between the slayer and the blood avenger according to these ordinances.
    \vs{25}'The congregation shall deliver the manslayer from the hand of the blood avenger, and the congregation shall restore him to his city of refuge to which he fled; and he shall live in it until the death of the high priest who was anointed with the holy oil.
\end{scripture}

\begin{scripture}[Deuteronomy 20:16-17]
    \vs{16}'Only in the cities of these peoples that the LORD your God is giving you as an inheritance, you shall not leave alive anything that breathes.
    \vs{17}'But you shall utterly destroy them, the Hittite and the Amorite, the Canaanite and the Perizzite, the Hivite and the Jebusite, as the LORD your God has commanded you,
\end{scripture}

\begin{scripture}[Exodus 22:1-3]
    \vs{1}'If a man steals an ox or a sheep and slaughters it or sells it, he shall pay five oxen for the ox and four sheep for the sheep.
    \vs{2}'If the thief is caught while breaking in and is struck so that he dies, there will be no bloodguiltiness on his account.
    \vs{3}'[But] if the sun has risen on him, there will be bloodguiltiness on his account. He shall surely make restitution; if he owns nothing, then he shall be sold for his theft.
\end{scripture}

\begin{scripture}[Exodus 21:12]
    \vs{12}'He who strikes a man so that he dies shall surely be put to death.
\end{scripture}

\begin{scripture}[Exodus 21:15-17]
    \vs{15}'He who strikes his father or his mother shall surely be put to death.
    \vs{16}'He who kidnaps a man, whether he sells him or he is found in his possession, shall surely be put to death.
    \vs{17}'He who curses his father or his mother shall surely be put to death.
\end{scripture}

\begin{scripture}[Leviticus 20:10]
    \vs{10}'If [there is] a man who commits adultery with another man's wife, one who commits adultery with his friend's wife, the adulterer and the adulteress shall surely be put to death.
\end{scripture}

\begin{scripture}[Leviticus 24:16]
    \vs{16}'Moreover, the one who blasphemes the name of the LORD shall surely be put to death; all the congregation shall certainly stone him. The alien as well as the native, when he blasphemes the Name, shall be put to death.
\end{scripture}

\begin{scripture}[John 19:10-11]
    \vs{10}So Pilate said to Him, 'You do not speak to me? Do You not know that I have authority to release You, and I have authority to crucify You?'
    \vs{11}Jesus answered, 'You would have no authority over Me, unless it had been given you from above; for this reason he who delivered Me to you has [the] greater sin.'
\end{scripture}

\begin{scripture}[Romans 13:1-7]
    \vs{1}Every person is to be in subjection to the governing authorities. For there is no authority except from God, and those which exist are established by God.
    \vs{2}Therefore whoever resists authority has opposed the ordinance of God; and they who have opposed will receive condemnation upon themselves.
    \vs{3}For rulers are not a cause of fear for good behavior, but for evil. Do you want to have no fear of authority? Do what is good and you will have praise from the same;
    \vs{4}for it is a minister of God to you for good. But if you do what is evil, be afraid; for it does not bear the sword for nothing; for it is a minister of God, an avenger who brings wrath on the one who practices evil.
    \vs{5}Therefore it is necessary to be in subjection, not only because of wrath, but also for conscience' sake.
    \vs{6}For because of this you also pay taxes, for [rulers] are servants of God, devoting themselves to this very thing.
    \vs{7}Render to all what is due them: tax to whom tax [is due]; custom to whom custom; fear to whom fear; honor to whom honor.
\end{scripture}

\begin{scripture}[Deuteronomy 2:19]
    \vs{19}'When you come opposite the sons of Ammon, do not harass them nor provoke them, for I will not give you any of the land of the sons of Ammon as a possession, because I have given it to the sons of Lot as a possession.'
\end{scripture}

\begin{scripture}[Leviticus 18:21]
    \vs{21}'You shall not give any of your offspring to offer them to Molech, nor shall you profane the name of your God; I am the LORD.
\end{scripture}

\begin{scripture}[Leviticus 20:1-5]
    \vs{1}Then the LORD spoke to Moses, saying,
    \vs{2}'You shall also say to the sons of Israel: 'Any man from the sons of Israel or from the aliens sojourning in Israel who gives any of his offspring to Molech, shall surely be put to death; the people of the land shall stone him with stones.
    \vs{3}'I will also set My face against that man and will cut him off from among his people, because he has given some of his offspring to Molech, so as to defile My sanctuary and to profane My holy name.
    \vs{4}'If the people of the land, however, should ever disregard that man when he gives any of his offspring to Molech, so as not to put him to death,
    \vs{5}then I Myself will set My face against that man and against his family, and I will cut off from among their people both him and all those who play the harlot after him, by playing the harlot after Molech.
\end{scripture}

\begin{scripture}[1 Kings 11:4-8]
    \vs{4}For when Solomon was old, his wives turned his heart away after other gods; and his heart was not wholly devoted to the LORD his God, as the heart of David his father [had been].
    \vs{5}For Solomon went after Ashtoreth the goddess of the Sidonians and after Milcom the detestable idol of the Ammonites.
    \vs{6}Solomon did what was evil in the sight of the LORD, and did not follow the LORD fully, as David his father [had done].
    \vs{7}Then Solomon built a high place for Chemosh the detestable idol of Moab, on the mountain which is east of Jerusalem, and for Molech the detestable idol of the sons of Ammon.
    \vs{8}Thus also he did for all his foreign wives, who burned incense and sacrificed to their gods.
\end{scripture}

\begin{scripture}[2 Kings 21:1-6]
    \vs{1}Manasseh was twelve years old when he became king, and he reigned fifty-five years in Jerusalem; and his mother's name was Hephzibah.
    \vs{2}He did evil in the sight of the LORD, according to the abominations of the nations whom the LORD dispossessed before the sons of Israel.
    \vs{3}For he rebuilt the high places which Hezekiah his father had destroyed; and he erected altars for Baal and made an Asherah, as Ahab king of Israel had done, and worshiped all the host of heaven and served them.
    \vs{4}He built altars in the house of the LORD, of which the LORD had said, 'In Jerusalem I will put My name.'
    \vs{5}For he built altars for all the host of heaven in the two courts of the house of the LORD.
    \vs{6}He made his son pass through the fire, practiced witchcraft and used divination, and dealt with mediums and spiritists. He did much evil in the sight of the LORD provoking [Him to anger].
\end{scripture}

\begin{scripture}[2 Kings 21:11-12]
    \vs{11}'Because Manasseh king of Judah has done these abominations, having done wickedly more than all the Amorites did who [were] before him, and has also made Judah sin with his idols;
    \vs{12}therefore thus says the LORD, the God of Israel, 'Behold, I am bringing [such] calamity on Jerusalem and Judah, that whoever hears of it, both his ears will tingle.
\end{scripture}

\begin{scripture}[2 Kings 21:16]
    \vs{16}Moreover, Manasseh shed very much innocent blood until he had filled Jerusalem from one end to another; besides his sin with which he made Judah sin, in doing evil in the sight of the LORD.
\end{scripture}

\begin{scripture}[2 Chronicles 28:1-4]
    \vs{1}Ahaz [was] twenty years old when he became king, and he reigned sixteen years in Jerusalem; and he did not do right in the sight of the LORD as David his father [had done].
    \vs{2}But he walked in the ways of the kings of Israel; he also made molten images for the Baals.
    \vs{3}Moreover, he burned incense in the valley of Ben-hinnom and burned his sons in fire, according to the abominations of the nations whom the LORD had driven out before the sons of Israel.
    \vs{4}He sacrificed and burned incense on the high places, on the hills and under every green tree.
\end{scripture}

\begin{scripture}[Deuteronomy 12:29-31]
    \vs{29}'When the LORD your God cuts off before you the nations which you are going in to dispossess, and you dispossess them and dwell in their land,
    \vs{30}beware that you are not ensnared to follow them, after they are destroyed before you, and that you do not inquire after their gods, saying, 'How do these nations serve their gods, that I also may do likewise?'
    \vs{31}'You shall not behave thus toward the LORD your God, for every abominable act which the LORD hates they have done for their gods; for they even burn their sons and daughters in the fire to their gods.
\end{scripture}

\begin{scripture}[Isaiah 10:1-2]
    \vs{1}Woe to those who enact evil statutes And to those who constantly record unjust decisions,
    \vs{2}So as to deprive the needy of justice And rob the poor of My people of [their] rights, So that widows may be their spoil And that they may plunder the orphans.
\end{scripture}

\begin{scripture}[Isaiah 5:20]
    \vs{20}Woe to those who call evil good, and good evil; Who substitute darkness for light and light for darkness; Who substitute bitter for sweet and sweet for bitter!
\end{scripture}

\begin{scripture}[Philippians 2:14-16]
    \vs{14}Do all things without grumbling or disputing;
    \vs{15}so that you will prove yourselves to be blameless and innocent, children of God above reproach in the midst of a crooked and perverse generation, among whom you appear as lights in the world,
    \vs{16}holding fast the word of life, so that in the day of Christ I will have reason to glory because I did not run in vain nor toil in vain.
\end{scripture}

\begin{scripture}[Matthew 5:13-16]
    \vs{13}'You are the salt of the earth; but if the salt has become tasteless, how can it be made salty [again]? It is no longer good for anything, except to be thrown out and trampled under foot by men.
    \vs{14}'You are the light of the world. A city set on a hill cannot be hidden;
    \vs{15}nor does [anyone] light a lamp and put it under a basket, but on the lampstand, and it gives light to all who are in the house.
    \vs{16}'Let your light shine before men in such a way that they may see your good works, and glorify your Father who is in heaven.
\end{scripture}

\begin{scripture}[Amos 1:13-15]
    \vs{13}Thus says the LORD, 'For three transgressions of the sons of Ammon and for four I will not revoke its [punishment], Because they ripped open the pregnant women of Gilead In order to enlarge their borders.
    \vs{14}'So I will kindle a fire on the wall of Rabbah And it will consume her citadels Amid war cries on the day of battle, And a storm on the day of tempest.
    \vs{15}'Their king will go into exile, He and his princes together,' says the LORD.
\end{scripture}

\begin{scripture}[Psalm 96:5]
    \vs{5}For all the gods of the peoples are idols, But the LORD made the heavens.
\end{scripture}

\begin{scripture}[Leviticus 18:24-30]
    \vs{24}'Do not defile yourselves by any of these things; for by all these the nations which I am casting out before you have become defiled.
    \vs{25}'For the land has become defiled, therefore I have brought its punishment upon it, so the land has spewed out its inhabitants.
    \vs{26}'But as for you, you are to keep My statutes and My judgments and shall not do any of these abominations, [neither] the native, nor the alien who sojourns among you
    \vs{27}(for the men of the land who have been before you have done all these abominations, and the land has become defiled);
    \vs{28}so that the land will not spew you out, should you defile it, as it has spewed out the nation which has been before you.
    \vs{29}'For whoever does any of these abominations, those persons who do [so] shall be cut off from among their people.
    \vs{30}'Thus you are to keep My charge, that you do not practice any of the abominable customs which have been practiced before you, so as not to defile yourselves with them; I am the LORD your God.''
\end{scripture}

\begin{scripture}[Isaiah 2:6-8]
    \vs{6}For You have abandoned Your people, the house of Jacob, Because they are filled [with influences] from the east, And [they are] soothsayers like the Philistines, And they strike [bargains] with the children of foreigners.
    \vs{7}Their land has also been filled with silver and gold And there is no end to their treasures; Their land has also been filled with horses And there is no end to their chariots.
    \vs{8}Their land has also been filled with idols; They worship the work of their hands, That which their fingers have made.
\end{scripture}

\begin{scripture}[Romans 12:2]
    \vs{2}And do not be conformed to this world, but be transformed by the renewing of your mind, so that you may prove what the will of God is, that which is good and acceptable and perfect.
\end{scripture}

\begin{scripture}[1 John 2:15-17]
    \vs{15}Do not love the world nor the things in the world. If anyone loves the world, the love of the Father is not in him.
    \vs{16}For all that is in the world, the lust of the flesh and the lust of the eyes and the boastful pride of life, is not from the Father, but is from the world.
    \vs{17}The world is passing away, and [also] its lusts; but the one who does the will of God lives forever.
\end{scripture}

\begin{scripture}[1 Peter 2:9-12]
    \vs{9}But you are A CHOSEN RACE, A royal PRIESTHOOD, A HOLY NATION, A PEOPLE FOR [God's] OWN POSSESSION, so that you may proclaim the excellencies of Him who has called you out of darkness into His marvelous light;
    \vs{10}for you once were NOT A PEOPLE, but now you are THE PEOPLE OF GOD; you had NOT RECEIVED MERCY, but now you have RECEIVED MERCY.
    \vs{11}Beloved, I urge you as aliens and strangers to abstain from fleshly lusts which wage war against the soul.
    \vs{12}Keep your behavior excellent among the Gentiles, so that in the thing in which they slander you as evildoers, they may because of your good deeds, as they observe [them], glorify God in the day of visitation.
\end{scripture}

\begin{scripture}[Micah 6:8]
    \vs{8}He has told you, O man, what is good; And what does the LORD require of you But to do justice, to love kindness, And to walk humbly with your God?
\end{scripture}

\begin{scripture}[Proverbs 31:8-9]
    \vs{8}Open your mouth for the mute, For the rights of all the unfortunate.
    \vs{9}Open your mouth, judge righteously, And defend the rights of the afflicted and needy.
\end{scripture}

\begin{scripture}[1 Samuel 15:22]
    \vs{22}Samuel said, 'Has the LORD as much delight in burnt offerings and sacrifices As in obeying the voice of the LORD? Behold, to obey is better than sacrifice, [And] to heed than the fat of rams.
\end{scripture}

\begin{scripture}[Deuteronomy 10:12-13]
    \vs{12}'Now, Israel, what does the LORD your God require from you, but to fear the LORD your God, to walk in all His ways and love Him, and to serve the LORD your God with all your heart and with all your soul,
    \vs{13}[and] to keep the LORD'S commandments and His statutes which I am commanding you today for your good?
\end{scripture}

\begin{scripture}[Proverbs 14:23]
    \vs{23}In all labor there is profit, But mere talk [leads] only to poverty.
\end{scripture}

\begin{scripture}[1 John 3:18]
    \vs{18}Little children, let us not love with word or with tongue, but in deed and truth.
\end{scripture}

\begin{scripture}[Ephesians 5:11]
    \vs{11}Do not participate in the unfruitful deeds of darkness, but instead even expose them;
\end{scripture}

\begin{scripture}[James 1:22-25]
    \vs{22}But prove yourselves doers of the word, and not merely hearers who delude themselves.
    \vs{23}For if anyone is a hearer of the word and not a doer, he is like a man who looks at his natural face in a mirror;
    \vs{24}for [once] he has looked at himself and gone away, he has immediately forgotten what kind of person he was.
    \vs{25}But one who looks intently at the perfect law, the [law] of liberty, and abides by it, not having become a forgetful hearer but an effectual doer, this man will be blessed in what he does.
\end{scripture}

\begin{scripture}[1 Peter 3:14-17]
    \vs{14}But even if you should suffer for the sake of righteousness, you are blessed. AND DO NOT FEAR THEIR INTIMIDATION, AND DO NOT BE TROUBLED,
    \vs{15}but sanctify Christ as Lord in your hearts, always [being] ready to make a defense to everyone who asks you to give an account for the hope that is in you, yet with gentleness and reverence;
    \vs{16}and keep a good conscience so that in the thing in which you are slandered, those who revile your good behavior in Christ will be put to shame.
    \vs{17}For it is better, if God should will it so, that you suffer for doing what is right rather than for doing what is wrong.
\end{scripture}

\begin{scripture}[Matthew 5:10-12]
    \vs{10}'Blessed are those who have been persecuted for the sake of righteousness, for theirs is the kingdom of heaven.
    \vs{11}'Blessed are you when [people] insult you and persecute you, and falsely say all kinds of evil against you because of Me.
    \vs{12}'Rejoice and be glad, for your reward in heaven is great; for in the same way they persecuted the prophets who were before you.
\end{scripture}

\begin{scripture}[1 Peter 4:12-16]
    \vs{12}Beloved, do not be surprised at the fiery ordeal among you, which comes upon you for your testing, as though some strange thing were happening to you;
    \vs{13}but to the degree that you share the sufferings of Christ, keep on rejoicing, so that also at the revelation of His glory you may rejoice with exultation.
    \vs{14}If you are reviled for the name of Christ, you are blessed, because the Spirit of glory and of God rests on you.
    \vs{15}Make sure that none of you suffers as a murderer, or thief, or evildoer, or a troublesome meddler;
    \vs{16}but if [anyone suffers] as a Christian, he is not to be ashamed, but is to glorify God in this name.
\end{scripture}

\begin{scripture}[John 16:33]
    \vs{33}'These things I have spoken to you, so that in Me you may have peace. In the world you have tribulation, but take courage; I have overcome the world.'
\end{scripture}

\begin{scripture}[John 17:14-16]
    \vs{14}'I have given them Your word; and the world has hated them, because they are not of the world, even as I am not of the world.
    \vs{15}'I do not ask You to take them out of the world, but to keep them from the evil [one].
    \vs{16}'They are not of the world, even as I am not of the world.
\end{scripture}

\begin{scripture}[Matthew 10:34-36]
    \vs{34}'Do not think that I came to bring peace on the earth; I did not come to bring peace, but a sword.
    \vs{35}'For I came to SET A MAN AGAINST HIS FATHER, AND A DAUGHTER AGAINST HER MOTHER, AND A DAUGHTER-IN-LAW AGAINST HER MOTHER-IN-LAW;
    \vs{36}and A MAN'S ENEMIES WILL BE THE MEMBERS OF HIS HOUSEHOLD.
\end{scripture}

\begin{scripture}[Romans 12:18]
    \vs{18}If possible, so far as it depends on you, be at peace with all men.
\end{scripture}

\begin{scripture}[Matthew 5:9]
    \vs{9}'Blessed are the peacemakers, for they shall be called sons of God.
\end{scripture}

\begin{scripture}[James 3:17-18]
    \vs{17}But the wisdom from above is first pure, then peaceable, gentle, reasonable, full of mercy and good fruits, unwavering, without hypocrisy.
    \vs{18}And the seed whose fruit is righteousness is sown in peace by those who make peace.
\end{scripture}

\begin{scripture}[1 Corinthians 1:18]
    \vs{18}For the word of the cross is foolishness to those who are perishing, but to us who are being saved it is the power of God.
\end{scripture}

\begin{scripture}[Galatians 1:10]
    \vs{10}For am I now seeking the favor of men, or of God? Or am I striving to please men? If I were still trying to please men, I would not be a bond-servant of Christ.
\end{scripture}

\begin{scripture}[John 15:18-20]
    \vs{18}'If the world hates you, you know that it has hated Me before [it hated] you.
    \vs{19}'If you were of the world, the world would love its own; but because you are not of the world, but I chose you out of the world, because of this the world hates you.
    \vs{20}'Remember the word that I said to you, 'A slave is not greater than his master.' If they persecuted Me, they will also persecute you; if they kept My word, they will keep yours also.
\end{scripture}

\begin{scripture}[Ephesians 5:11]
    \vs{11}Do not participate in the unfruitful deeds of darkness, but instead even expose them;
\end{scripture}

\begin{scripture}[Leviticus 19:15]
    \vs{15}'You shall do no injustice in judgment; you shall not be partial to the poor nor defer to the great, but you are to judge your neighbor fairly.
\end{scripture}

\begin{scripture}[Leviticus 19:18]
    \vs{18}'You shall not take vengeance, nor bear any grudge against the sons of your people, but you shall love your neighbor as yourself; I am the LORD.
\end{scripture}

\begin{scripture}[Matthew 22:37-40]
    \vs{37}And He said to him, ''YOU SHALL LOVE THE LORD YOUR GOD WITH ALL YOUR HEART, AND WITH ALL YOUR SOUL, AND WITH ALL YOUR MIND.'
    \vs{38}'This is the great and foremost commandment.
    \vs{39}'The second is like it, 'YOU SHALL LOVE YOUR NEIGHBOR AS YOURSELF.'
    \vs{40}'On these two commandments depend the whole Law and the Prophets.'
\end{scripture}

\begin{scripture}[Luke 10:29-37]
    \vs{29}But wishing to justify himself, he said to Jesus, 'And who is my neighbor?'
    \vs{30}Jesus replied and said, 'A man was going down from Jerusalem to Jericho, and fell among robbers, and they stripped him and beat him, and went away leaving him half dead.
    \vs{31}'And by chance a priest was going down on that road, and when he saw him, he passed by on the other side.
    \vs{32}'Likewise a Levite also, when he came to the place and saw him, passed by on the other side.
    \vs{33}'But a Samaritan, who was on a journey, came upon him; and when he saw him, he felt compassion,
    \vs{34}and came to him and bandaged up his wounds, pouring oil and wine on [them]; and he put him on his own beast, and brought him to an inn and took care of him.
    \vs{35}'On the next day he took out two denarii and gave them to the innkeeper and said, 'Take care of him; and whatever more you spend, when I return I will repay you.'
    \vs{36}'Which of these three do you think proved to be a neighbor to the man who fell into the robbers' [hands]?'
    \vs{37}And he said, 'The one who showed mercy toward him.' Then Jesus said to him, 'Go and do the same.'
\end{scripture}

\begin{scripture}[James 2:8-9]
    \vs{8}If, however, you are fulfilling the royal law according to the Scripture, 'YOU SHALL LOVE YOUR NEIGHBOR AS YOURSELF,' you are doing well.
    \vs{9}But if you show partiality, you are committing sin [and] are convicted by the law as transgressors.
\end{scripture}

\begin{scripture}[Galatians 3:28]
    \vs{28}There is neither Jew nor Greek, there is neither slave nor free man, there is neither male nor female; for you are all one in Christ Jesus.
\end{scripture}

\begin{scripture}[Galatians 5:14]
    \vs{14}For the whole Law is fulfilled in one word, in the [statement], 'YOU SHALL LOVE YOUR NEIGHBOR AS YOURSELF.'
\end{scripture}

\begin{scripture}[Romans 13:8-10]
    \vs{8}Owe nothing to anyone except to love one another; for he who loves his neighbor has fulfilled [the] law.
    \vs{9}For this, 'YOU SHALL NOT COMMIT ADULTERY, YOU SHALL NOT MURDER, YOU SHALL NOT STEAL, YOU SHALL NOT COVET,' and if there is any other commandment, it is summed up in this saying, 'YOU SHALL LOVE YOUR NEIGHBOR AS YOURSELF.'
    \vs{10}Love does no wrong to a neighbor; therefore love is the fulfillment of [the] law.
\end{scripture}

\begin{scripture}[Matthew 5:43-44]
    \vs{43}'You have heard that it was said, 'YOU SHALL LOVE YOUR NEIGHBOR and hate your enemy.'
    \vs{44}'But I say to you, love your enemies and pray for those who persecute you,
\end{scripture}
